\documentclass[12pt, letterpaper, final]{article}

% Page Layout configurations.
\usepackage[margin=1.25in]{geometry} % Adjust page margins if needed

% Fonts and text settings
\usepackage[T1]{fontenc} % sets the font encoding of the document to T1, improving various glyph representations
%\usepackage[default]{sourceserifpro} % set Document font

% Custon Font section
\usepackage{fontspec}
\usepackage{anyfontsize}
\setmainfont{Book Antiqua}
\usepackage{parskip} % for better paragraph separation
\usepackage{enumitem} % for better lists
\usepackage[ampersand]{easylist}

% Images and floats configurations.
%\usepackage{graphicx} % For including images
%\usepackage{subcaption}  % for supporting sub-figures and sub-tables within a single figure or table environment
%\captionsetup[figure]{font=small,labelfont=bf}
%\usepackage{float} % Improved floating for Tables and figures

% Code formatting
%\usepackage{minted} % For code style

% Additional features and utilities.
\usepackage[obeyDraft]{todonotes}
\setlength{\marginparwidth}{2cm}
\usepackage{draftwatermark}
\usepackage{authblk} % for better author block
\usepackage{titling} % for better titling
\usepackage{xcolor}     % for colors
\usepackage{typed-checklist} % for checklists
\usepackage[document]{ragged2e} % for better ragged right

% Hyperlinks
\usepackage[
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue,
]{hyperref} % for hyperlinks

% adjust page top
\setlength{\droptitle}{-9em}

% Custom macros used in this example document
\newcommand{\doclink}[2]{\href{#1}{#2}\footnote{\url{#1}}}

\title{An Onerous Yoke}
\author{}
\date{}

\begin{document}
\maketitle
\vspace{-1in}

\begin{abstract}
    \begin{center}
        An ode to Calendar events and moderation.
    \end{center}
\end{abstract}

Howdy, IS\textemdash please give my thanks to Zac for solving all my problems last time I reached out.
What a hero!

The new events calendar tells me to contact you if I have questions.
Well, I have a question.
Or maybe it's more of a comment.
Perhaps it even qualifies as a complaint, a complaint I would like to see resolved.
I find new event calendar's review moderation step an offensively paternalistic time-suck.
To be forced to wait for someone who is not in my immediate supervisory position to evaluate my posts and revisions to ensure they are “clear,” “well-categorized,” and “appropriate” is a waste of my time, a waste of your time, and it implies a waste of the many years I've invested in learning how to communicate effectively with my fellow humans.
To be forced to wait, as the calendar guide indicates, {\large ONE TO TWO DAYS(!!!)} for a revision to be approved and posted is an absolutely ridiculous, unreasonable expectation in an age when I can have an inflatable tyrannosaurus rex costume shipped to my house in 24 hours.
I know, I know\textemdash it rarely takes that long for an event to be approved.
Doesn't matter\textemdash it's the principle of the thing.

So I have a few questions:

Number one of course: how can we remove this {\Huge onerous yoke} of moderation from my neck?

Number two through the rest: whose idea was this particular quality control mechanism and how might I sit down with them to discuss alternative ways to ensure calendar submissions are up to snuff?
Because, seriously, in whose service is it intended to operate? Surely not mine.

As an “officer” for an organization, I am the one with knowledge of my audience, and I am the one who is responsible for effective event promotion.
If it is causing me more headaches than it's curing, it's not helping me do my job any better or more efficiently or more effectively.
It's just a twig in my gizzard.

I ain't mad at 'cha.
No, I know you have the power to help me end this \\misery\ldots or at least you know someone who does.
If necessary, I'd be glad to come in and talk with any one of the wizards down there to get this evil spell removed.
Can you help me out here?
\end{document}
